Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-08-29 paper/main.tex
add idea to discussion
remove todo in heading
add more notes for introduction

%###################################################################################################
\section{Introduction}
\label{section:introduction}

@@

%###################################################################################################
\section{Application to \textit{E.Coli.} growing on Agar (TODO)}

@@

\begin{itemize}
    \item Highlight methodological advancements
    \item Constructed Model which already combines many effects; extend this even further
    \item Proof of concept: Able to fit individual parameters of the agents; can be extend this?
    \item Provide software package which combines all functionality and is readily available
\end{itemize}

>>>>

%###################################################################################################
\section{Introduction}

General comments on \acp{abm} and their problems
\begin{itemize}
    \item \aclp{abm} are used for many purposes
    \item describe current way of estimating parameters; compare distributions to each other; no idea if
          individual parameters are correct
    \item challenge: estimate their parameters
    \item challenge: construct minimal models (requires flexibility)
\end{itemize}

General remarks about the steps in this work
\begin{itemize}
    \item Use rod-shaped bacteria as model system
    \item Clear separation between different components (link to overview)
    \item This separation allows us to generalize the type of approach and apply to other models
    \item think of as a "blueprint" for estimating parameters for \acp{abm}
\end{itemize}

Experimental observations: rod-shaped bacteria
\begin{itemize}
    \item growth + division "distinct mechanical properties", MreB
    \item bendiness (not much studied)
    \item individual parameters (i.e. growth rates)
    \item adhesion to each other
\end{itemize}

Computational studies of rod-shaped bacteria
\begin{itemize}
    \item not so many models for rod-shaped bacteria
    \item could include more effects such as bending
    \item almost no efforts to estimate parameters with individual-based models
    \item although many things known no "generalized mechanical model" constructed for rod-shaped bacteria
\end{itemize}

\section{Introduction (old)}

@@

%###################################################################################################
\section{Application to \textit{E.Coli.} growing on Agar}

@@

\begin{itemize}
    \item Highlight methodological advancements
    \item Constructed Model which already combines many effects; extend this even further
    \item can now use classical methods: sensitivity-analysis, likelihood estimators and uncertainty quantification
    \item Proof of concept: Able to fit individual parameters of the agents; can be extend this?
    \item Provide software package which combines all functionality and is readily available
\end{itemize}
